A Kochen-Specker system has at least 22 vectors

### 2015-05-19 paper/main.tex
paper: if -> is
paper: neater sentence
paper: add more graphs

Before we continue, we would like to make two remarks.
\begin{enumerate}
\item
There is an inconsistency in the literature on how to count the number
of points in a Kochen-Specker system.  One way is to take the minimal
number of points required to be non-010-colorable.
This is how we count in this paper.
Another way is to require that for every pair of orthogonal points
in the system, there is a third point orthogonal to both.
This way of counting is for example used in~\cite{pavivcic}.
\item
We consider three-dimensional Kochen-Specker systems
for two reasons.
First, every 3-dimensional system can be seen as a higher-dimensional
            system.   The converse if false.
Secondly, the size of the least Kochen-Specker system
            in dimension 4 and higher has already been found.\cite{pavivcic}
            The three-dimensional case is still open.
\end{enumerate}

@@

\begin{proof}
    Given two non antipodal points~$v\neq w$.
    See the figure on the right.
    Consider the points orthogonal to~$v$.
    This is a great circle.
    The points orthogonal to~$w$ is a different great circle.
    They intersect in precisely two antipodal points.
    Hence, if~$c$ and~$d$ are both orthogonal to~$v$ and~$w$,
    then~$c$ and~$d$ are equivalent.
    Therefore, an embeddable graph cannot contain a square.
\end{proof}

@@

Although these restrictions are theoretically pleasing,
they seem to be of little use as a practical restriction.
Concerning excluding disconnected graphs:
% TODO Add argument or computation for {2,3}-connected
% TODO note that restricting to (bi/tri)-connected is a waste of time
% TODO add graph 
\begin{comp}
    There are five non-isomorphic minimal
    squarefree connected graphs
    with minimal vertex order 3 and they have 10 vertices.
    \footnote{They are the first five graphs
            listed on:
    \url{http://kochen-specker.info/smallGraphs/}.}
\end{comp}
\begin{corollary}\label{cor:littlecon}
    Any disconnected
    squarefree graph with minimal vertex order 3
    has at least 20 vertices, for it has two connected components,
    each with at least 10 vertices.
    With 20 vertices, there are exactly 25 of these.
\end{corollary}
This justifies, at this stage, not checking for connectedness.
Similarly, we believe there are very few connected but not
edge-biconnected graphs.

>>>>

Before we continue, we would like to make two remarks.
\begin{enumerate}
\item
There is an inconsistency in the literature on how to count the number
of points in a Kochen-Specker system.  One way is to take the minimal
number of points required to be non-010-colorable.
This is how we count in this paper.
Another way is to require that for every pair of orthogonal points
in the system, there is a third point orthogonal to both.
This way of counting is for example used in~\cite{pavivcic}.
\item
We consider three-dimensional Kochen-Specker systems
for two reasons.
First, every 3-dimensional system can be seen as a higher-dimensional
            system.   The converse is false.
Secondly, the size of the least Kochen-Specker system
            in dimension 4 and higher has already been found.\cite{pavivcic}
            The three-dimensional case is still open.
\end{enumerate}

@@

\begin{proof}
    Given two non antipodal points~$v\neq w$.
    See the figure on the right.
    Consider the points orthogonal to~$v$.
    This is a great circle.
    The points orthogonal to~$w$ is a different great circle.
    They intersect in precisely two antipodal points.
    Hence, if~$c$ and~$d$ are points, both orthogonal to~$v$ and~$w$,
    then~$c$ and~$d$ are equivalent.
    Therefore, an embeddable graph cannot contain a square.
\end{proof}

@@

Although these restrictions are theoretically pleasing,
they seem to be of little use as a practical restriction.
Concerning excluding disconnected graphs:
% TODO Add argument or computation for {2,3}-connected
% TODO note that restricting to (bi/tri)-connected is a waste of time
% TODO add graph 
\begin{comp}
    There are five non-isomorphic minimal
    squarefree connected graphs
    with minimal vertex order 3 and they have 10
    vertices.\footnote{They are the first five graphs
            listed on:
    \url{http://kochen-specker.info/smallGraphs/}.}
    Three of them are embeddable and shown below.
    The remaining two
    are depicted in Comptutation~\ref{comp:unemb20}.
\begin{center}
\begin{tikzpicture}[thick,scale=1.0,
    p/.style={circle, draw, fill=white,
                    inner sep=0pt, minimum width=5pt}]

        \draw
                (30:0.5) node[p]{} -- (65:1.3) node[p]{}
                (30:0.5)  -- (25:1.3) node[p]{}
                (65:1.3)  -- (25:1.3)

                (150:0.5) node[p]{} -- (155:1.3) node[p]{}
                (150:0.5)  -- (115:1.3) node[p]{}
                (155:1.3)  -- (115:1.3)

            (90:0.5) node[p]{}
            (90:-0.5) node[p]{}
            (115:1.3) -- (65:1.3) -- (90:0.5) -- (115:1.3)
            (90:0.5) -- (90:-0.5)
            (350:1) node[p]{}
            (190:1) node[p]{}
            (155:1.3) -- (190:1) -- (270:0.5) -- (350:1) -- (25:1.3)
            (150:0.5) -- (350:1)
            (30:0.5) -- (190:1)
            ;
    \end{tikzpicture}
    \qquad
    \begin{tikzpicture}[thick,scale=1.0,
    p/.style={circle, draw, fill=white,
                    inner sep=0pt, minimum width=5pt}]
        \draw
            \foreach \x in {0,60,120,180,240,300} {
                (\x:1.3) node[p]{} -- (\x+60:1.3) node[p]{}
            }
	(0,0) node[p]{} -- (270:0.5) node[p]{}
	(0,0) -- (45:0.5) node[p]{} -- (300:1.3)
	(0:0) -- (135:0.5) node[p]{} -- (240:1.3)
	(180:1.3) -- (270:0.5) -- (0:1.3)
	(60:1.3) -- (135:0.5)
	(120:1.3) -- (45:0.5);
    \end{tikzpicture}
    \qquad
    \begin{tikzpicture}[thick,scale=1.0,
    p/.style={circle, draw, fill=white,
                    inner sep=0pt, minimum width=5pt}]
                            \draw
                (30:0.5) node[p]{} -- (65:1.3) node[p]{}
                (30:0.5)  -- (25:1.3) node[p]{}
                (65:1.3)  -- (25:1.3)
                (150:0.5) node[p]{} -- (155:1.3) node[p]{}
                (150:0.5)  -- (115:1.3) node[p]{}
                (155:1.3)  -- (115:1.3)
                (90:1) node[p]{}
                (90:-0.5) node[p]{}
                (65:1.3) -- (90:1) -- (115:1.3)
                (90:1) -- (90:-0.5)
                (350:1) node[p]{}
                (190:1) node[p]{}
                (155:1.3) -- (190:1) -- (270:0.5) -- (350:1) -- (25:1.3)
                (150:0.5) -- (350:1)
                (30:0.5) -- (190:1) ;
\end{tikzpicture}
\end{center}
\end{comp}
\begin{corollary}\label{cor:littlecon}
    Any disconnected
    squarefree graph with minimal vertex order 3
    has at least 20 vertices, for it has two connected components,
    each with at least 10 vertices.
    With 20 vertices, there are exactly 25 of these.
\end{corollary}
This justifies, at this stage, not checking for connectedness.
Similarly, we believe there are very few connected but not
edge-biconnected graphs.
